RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-03-17 inst/doc/pubs/manuscript.Rmd
a few writing edits
draft updated, examples all seem to run at this time for me anyway

``{r}
plot(phy)
```

@@

```{r }
nex <- nexml_read("comp_analysis.xml")
get_characters(nex)
```

@@

```{r}
birds <- taxize_nexml(birds, "NCBI")
```

@@

To illustrate metadata access, we begin by reading in a NeXML file.

```{r } 
S100 <- nexml_read("https://raw.github.com/rvosa/supertreebase/master/data/treebase/S100.xml")
```

A call to the nexml object prints some metadata summarizing the data structure:

```{r }
S100
```

@@

```{r}
meta <- get_metadata(S100) 
```

This returns a named list of available metadata. We can see the kinds
of metadata recorded from the names:

```{r}
names(meta)
```

@@

```{r}
meta[["dc:title"]]
meta[["dc:publisher"]]
```

@@

```{r}
prefixes <- get_namespaces(S100)
prefixes["dc"]
```

@@

```{r}
get_citation(S100)
```

```{r}
get_taxa(S100)
```

@@

```{r} 
otu_meta <- get_metadata(S100, level="otu")
otu_meta[1:2]
```

@@

```{r}
rdf <- get_rdf(S100)
```

@@

```{r eval = FALSE}
id <- nexml_publish(nexml, visibility = "public", repository="figshare")
```

>>>>

```{r eval=FALSE}
plot(phy)
```

@@

```{r }
comp_analysis <- system.file("examples", "comp_analysis.xml", package="RNeXML")
nex <- nexml_read(comp_analysis)
get_characters(nex)
```

@@

```{r message=FALSE, results='hide'}
birds <- taxize_nexml(birds, "NCBI")
```

@@

A call to the nexml object prints some metadata summarizing the data structure: <!-- need to make this method faster!-->

```{r }
birds
```

@@

```{r}
meta <- get_metadata(birds) 
```

This returns a named list of available metadata. We can see the kinds
of metadata recorded from the names (showing the first 4):

```{r}
names(meta)[1:4]
```

@@

```{r}
meta[["dc:title"]]
```

@@

@@

```{r}
get_citation(birds)
```

```{r}
get_taxa(birds)
```

@@

```{r} 
otu_meta <- get_metadata(birds, level="otu")
otu_meta[1:4]
```

@@

```{r}
rdf <- get_rdf(birds)
```

@@

```{r eval = FALSE}
doi <- nexml_publish(birds, visibility = "public", repository="figshare")
```
